Determining the alternatives for scalar implicature

### 2016-01-27 Paper/Paper.tex
tweaked intro

How much of what we mean comes from the words that go unsaid? As
listeners, the ability to enrich meaning in context is an indispensible
component of succesful communication. For example, listeners commonly
enrich the meaning of the scalar item \emph{some} to \emph{some but not
all} in sentences like ``Alice ate some of the cookies'' (Grice, 1975;
Horn, 1984; Levinson, 2000). These inferences, called \emph{scalar
implicatures}, have been an important test case for understanding
pragmatic inferences more generally. A Gricean account of this phenomena
assumes listeners reason about the meaning the speaker intended by
incorporating knowledge about a) alternative scalar items a speaker
could have used (such as \emph{all}) and b) the relative informativity
of using such alternatives (Grice, 1975). According to this account, a
listener will infer that the speaker must have intended that Alice did
not eat \emph{all} the cookies because it would have been
\emph{underinformative} for the speaker to use \emph{some} when
\emph{all} could have been used.

>>>>

How much of what we mean comes from the words that go unsaid? As
listeners, the ability to enrich a speaker's meaning in context is an
indispensable component of successful communication. For example,
listeners commonly enrich the meaning of the scalar item \emph{some} to
\emph{some but not all} in sentences like ``Alice ate some of the
cookies'' (Grice, 1975; Horn, 1984; Levinson, 2000). These inferences,
called \emph{scalar implicatures}, have been an important test case for
understanding pragmatic inferences more generally. A Gricean account of
this phenomena assumes listeners reason about the meaning the speaker
intended by incorporating knowledge about a) alternative scalar items a
speaker could have used (such as \emph{all}) and b) the relative
informativity of using such alternatives (Grice, 1975). According to
this account, a listener will infer that the speaker must have intended
that Alice did not eat \emph{all} the cookies because it would have been
\emph{underinformative} for the speaker to use \emph{some} when
\emph{all} could have been used.
